Nobody expects the Spanish Inquisition: Which events drive topic change in Australian parliaments?

### 2018-09-15 outputs/docs/events/svm-rmarkdown-article-example.Rmd
Update the topic modelling and minor improvements to the paper

---
title: "Nobody expects the Spanish Inquisition: Which events drive topic change in Australian parliaments?"
author:
  - Monica Alexander^[University of Toronto, Statistical Sciences and Sociology Departments, \texttt{monica.alexander@utoronto.ca}.]
  - Rohan Alexander^[Australian National University, Research School of Economics, \texttt{rohan.alexander@anu.edu.au}.]
date: "`r format(Sys.time(), '%d %B %Y')`"
fontsize: 12pt
output: 
  pdf_document:
    number_sections: true
bibliography: ../bibliography.bib
abstract: |
  We use a structural text model to explore the impact of various events on what was said in Australian state and Commonwealth parliaments from the mid-1800s through to 2017. We find that 1) changes of government where the party in power also changes, result in significant changes in topics discussed in parliament, but when the party does not change the topics are unchanged; 2) polling results do not have a significant effect; 3) economic changes, such as financial crises have a significant effect; and 4) other events, such as an unexpected attack tend not to have a prolonged change.

---

@@

# Introduction
New governments often go out of their way to be different to the governments they replace. For instance, Kevin Rudd's apology to Indigenous Australians was supported by all living former Prime Ministers apart from his immediate predecessor. Similarly,  Similarly, significant events can alter the course of a government. For instance, consider the change in the Howard government after the 9/11 attacks. However it is not so clear which events drive changes in topics, for instance, do they change when the government is replaced by another of its own party? And which events are temporary, for instance when an economic crisis abates, do the topics return to pre-crisis levels?

@@

# Data
Following the example of the UK, a text-based record of what was said in Australian parliaments called Hansard has been regularly made available since their establishment. While Hansard is not necessarily verbatim, it is considered close enough for text-as-data purposes. For instance, @Mollin2008 found that in the case of the UK Hansard the differences would only affect specialised linguistic analysis. @Edwards2016 examined Australia, New Zealand and the UK, and found that changes were usually made by those responsible for creating the Hansard record, instead of the parliamentarians. Both these findings provide reassurance that differences between Hansard and a verbatim record would not be meaningful for this paper.

The parliaments generally make their hansard records available online in PDF formats that can be processed by text readers such as @Ooms2018pdftools. Some records such as the early days of the New South Wales parliament have yet to be put through a professional OCR process, although the Google Tesseract engine as implemented by @Ooms2018tesseract can be used to provide a useful first-pass if necessary. Hansard records that are still images are not used in this analysis (see the Appendix for more details).

Hansard records are available for all six Australian states and the Commonwealth although the period varies (Table 1). Here we focus on the lower houses although a similar analysis is possible in a bicameral setting.

@@

We start with the PDFs that have been through an OCR process (or compiled more recently using software that makes them readable by default) as supplied by various parliaments (see the Appendix for specific sources). We then use the \texttt{PDFtools} R package of @Ooms2018pdftools to extract these as text-based CSV records, and clean the records using functions from the \texttt{Tidyverse} R package of @WickhamHadleyTidyverse, the \texttt{Tidytext} R package of @SilgeRobinson2016 and the [INSERT OTHERS]. The result is a

@@

```{r topicsoverdocuments, cache = TRUE, echo=FALSE, out.width='.49\\linewidth', fig.cap = "Probability distributions over topics", fig.show = 'hold'}
document_1 <- tibble(
  Topics = c(
  "topic 1", "topic 2", "topic 3", "topic 4", "topic 5"
  ),
  Probability = c(0.40, 0.40, 0.1, 0.05, 0.05)
  )

@@

par(mfrow=c(2,1))
ggplot(document_1, aes(Topics, Probability)) +
  geom_point() +
  theme_classic() +
  labs(title = "Distribution over topics for Document 1") +
  coord_cartesian(ylim = c(0, 0.4))

ggplot(document_2, aes(Topics, Probability)) +
  geom_point() +
  theme_classic() +
  labs(title = "Distribution over topics for Document 2") +
  coord_cartesian(ylim = c(0, 0.4))
```

@@

# Appendix
## Selection of number of topics

@@

>>>>

---
output: 
  pdf_document:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: svm-latex-ms.tex
title: "Nobody expects the Spanish Inquisition: Which events drive topic change in Australian parliaments?"
thanks: "Thank you to John Tang, Zach Ward, Tim Hatton and Martine Mariotti for their helpful comments, guidance and suggestions. **Version as of**: `r format(Sys.time(), '%B %d, %Y')`; **Comments welcome**: rohan.alexander@anu.edu.au"
author:
- name: Monica Alexander
  affiliation: University of Toronto
- name: Rohan Alexander
  affiliation: Australian National University
abstract: "We use a structural text model to explore the effect of various events on what was said in Australian state and federal parliaments from the mid-1800s through to 2017. We find that: 1) changes of government are associated with topic changes only when there is also a change in the party in power; 2) polling results appear dissociated from parliamentary topics; 3) economic changes, such as financial crises have a significant effect; and 4) other events, such as an unexpected attack tend not to have a prolonged change."
keywords: "text analysis, politics, Australia"
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 12pt
# spacing: double
bibliography: ../bibliography.bib
biblio-style: apsr
endnote: no
---

@@

# Introduction
New governments often go to some trouble to be different from the governments they replace. For instance, Kevin Rudd's apology to Indigenous Australians was not supported by John Howard, and one of Tony Abbott's first acts was to repeal Rudd's carbon tax. Similarly, significant events can alter the course of a government. For instance, consider the change in the Howard government after the 9/11 attacks or the 2002 Bali bombings. However it is not so clear which events drive changes in topics, for instance, do they change when the government is replaced by another of its own party? And which events are temporary, for instance when an economic crisis abates, do the topics return to pre-crisis levels?

@@

# Data
Following the example of the UK a text record called Hansard of what was said in Australian parliaments has been made available since their establishment.[^1] Hansard records are an increasingly popular source of data as new methods and reduced computational costs make larger-scale analysis easier. For instance, the digitisation of the Canadian Hansard, @BeelenEtc2017, allowed @Whyte2017 to examine whether parliamentary disruptions in Canada increased between 1926 and 2015. In the UK, @Duthie2016 analysed Hansard records to examine which politicians made supportive or aggressive statements toward other politicians between 1979 and 1990, and @Willis2017 examined how politicians understood climate change. In New Zealand, @Curran2017 modelled the topics discussed between 2003 and 2016, and @Graham2016 examined unparliamentary language between 1890 and 1950.

Australian Hansard records have been analysed for various purposes, but usually not at scale. For instance, @Rasiah2010 examines Hansard records for the Australian House of Representatives to examine whether politicians attempted to evade questions about Iraq during February and March 2003. @GansLeigh2012 examined Australian Hansard records by hand to associate mentions by politicians of certain public intellectuals with neutral or positive sentiment.

[^1]: While Hansard is not necessarily verbatim, it is considered close enough for text-as-data purposes. For instance, @Mollin2008 found that in the case of the UK Hansard the differences would only affect specialised linguistic analysis. @Edwards2016 examined Australia, New Zealand and the UK, and found that changes were usually made by those responsible for creating the Hansard record, instead of the parliamentarians. Both these findings provide reassurance that differences between Hansard and a verbatim record would not be meaningful for this paper.

The Australian parliaments generally make their Hansard records available online as PDFs that can be downloaded. The Federal parliament additionally makes XML records available for years between 1901 and 1980 as well as from 1997. There are roughly 65,000 **(UPDATE)** hansard records available across the chambers of the state and federal parliaments (Table 1) **(UPDATE NUMBERING)**. As with any larger-scale data process, there are many issues with this dataset of PDFs and the known ones are detailed in the Appendix.

@@

The PDFs were processed using the \texttt{PDFtools} R package of @Ooms2018pdftools. A small proportion of the Hansard records had not been put through a professional OCR process and although the Google Tesseract engine as implemented by @Ooms2018tesseract provided some useful data, these were not used in this analysis.

to extract these as text-based CSV records, and clean the records using functions from the \texttt{Tidyverse} R package of @WickhamHadleyTidyverse, the \texttt{Tidytext} R package of @SilgeRobinson2016 and the [INSERT OTHERS]. The result is a

@@

```{r topicsoverdocuments, cache = TRUE, echo=FALSE, fig.cap = "Probability distributions over topics"}
document_1 <- tibble(
  Topics = c(
  "topic 1", "topic 2", "topic 3", "topic 4", "topic 5"
  ),
  Probability = c(0.40, 0.40, 0.1, 0.05, 0.05)
  )

@@

# par(mfrow=c(2,1))
ggplot(document_1, aes(Topics, Probability)) +
  geom_point() +
  theme_classic() +
  labs(title = "Distribution over topics for Document 1") +
  coord_cartesian(ylim = c(0, 0.4))
ggplot(document_2, aes(Topics, Probability)) +
  geom_point() +
  theme_classic() +
  labs(title = "Distribution over topics for Document 2") +
  coord_cartesian(ylim = c(0, 0.4))
```

@@

# Appendix

@@

## Dataset issues
Which PDFs are missing or have no content, etc.

## PDF to CSV issues
Insert graph of stop words over time.

## Selection of number of topics

### 2018-09-15 outputs/docs/events/svm-rmarkdown-article-example.tex
Update the topic modelling and minor improvements to the paper

\title{Nobody expects the Spanish Inquisition: Which events drive topic change
in Australian parliaments? \thanks{Thank you to X, Y, Z and Y for their helpful comments, guidance and
suggestions. \textbf{Version as of}: September 13, 2018;
\textbf{Comments welcomed}:
\href{mailto:rohan.alexander@anu.edu.au}{\nolinkurl{rohan.alexander@anu.edu.au}}}  }

@@

New governments often go to some trouble to be different to the
governments they replace. For instance, Kevin Rudd's apology to
Indigenous Australians was supported by all living former Prime
Ministers apart from his immediate predecessor. Similarly, Similarly,
significant events can alter the course of a government. For instance,
consider the change in the Howard government after the 9/11 attacks.
However it is not so clear which events drive changes in topics, for
instance, do they change when the government is replaced by another of
its own party? And which events are temporary, for instance when an
economic crisis abates, do the topics return to pre-crisis levels?

@@

Following the example of the UK, a text-based record of what was said in
Australian parliaments called Hansard has been regularly made available
since their establishment. While Hansard is not necessarily verbatim, it
is considered close enough for text-as-data purposes. For instance,
\citet{Mollin2008} found that in the case of the UK Hansard the
differences would only affect specialised linguistic analysis.
\citet{Edwards2016} examined Australia, New Zealand and the UK, and
found that changes were usually made by those responsible for creating
the Hansard record, instead of the parliamentarians. Both these findings
provide reassurance that differences between Hansard and a verbatim
record would not be meaningful for this paper.

The parliaments generally make their hansard records available online in
PDF formats that can be processed by text readers such as
\citet{Ooms2018pdftools}. Some records such as the early days of the New
South Wales parliament have yet to be put through a professional OCR
process, although the Google Tesseract engine as implemented by
\citet{Ooms2018tesseract} can be used to provide a useful first-pass if
necessary. Hansard records that are still images are not used in this
analysis (see the Appendix for more details).

Hansard records are available for all six Australian states and the
Commonwealth although the period varies (Table 1). Here we focus on the
lower houses although a similar analysis is possible in a bicameral
setting.

@@

We start with the PDFs that have been through an OCR process (or
compiled more recently using software that makes them readable by
default) as supplied by various parliaments (see the Appendix for
specific sources). We then use the \texttt{PDFtools} R package of
\citet{Ooms2018pdftools} to extract these as text-based CSV records, and
clean the records using functions from the \texttt{Tidyverse} R package
of \citet{WickhamHadleyTidyverse}, the \texttt{Tidytext} R package of
\citet{SilgeRobinson2016} and the {[}INSERT OTHERS{]}. The result is a

@@

@@

@@

>>>>

\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}

\title{Nobody expects the Spanish Inquisition: Which events drive topic change
in Australian parliaments? \thanks{Thank you to John Tang, Zach Ward, Tim Hatton and Martine Mariotti for
their helpful comments, guidance and suggestions. \textbf{Version as
of}: September 15, 2018; \textbf{Comments welcome}:
\href{mailto:rohan.alexander@anu.edu.au}{\nolinkurl{rohan.alexander@anu.edu.au}}}  }

@@

New governments often go to some trouble to be different from the
governments they replace. For instance, Kevin Rudd's apology to
Indigenous Australians was not supported by John Howard, and one of Tony
Abbott's first acts was to repeal Rudd's carbon tax. Similarly,
significant events can alter the course of a government. For instance,
consider the change in the Howard government after the 9/11 attacks or
the 2002 Bali bombings. However it is not so clear which events drive
changes in topics, for instance, do they change when the government is
replaced by another of its own party? And which events are temporary,
for instance when an economic crisis abates, do the topics return to
pre-crisis levels?

@@

Following the example of the UK a text record called Hansard of what was
said in Australian parliaments has been made available since their
establishment.\footnote{While Hansard is not necessarily verbatim, it is
  considered close enough for text-as-data purposes. For instance,
  \citet{Mollin2008} found that in the case of the UK Hansard the
  differences would only affect specialised linguistic analysis.
  \citet{Edwards2016} examined Australia, New Zealand and the UK, and
  found that changes were usually made by those responsible for creating
  the Hansard record, instead of the parliamentarians. Both these
  findings provide reassurance that differences between Hansard and a
  verbatim record would not be meaningful for this paper.} Hansard
records are an increasingly popular source of data as new methods and
reduced computational costs make larger-scale analysis easier. For
instance, the digitisation of the Canadian Hansard,
\citet{BeelenEtc2017}, allowed \citet{Whyte2017} to examine whether
parliamentary disruptions in Canada increased between 1926 and 2015. In
the UK, \citet{Duthie2016} analysed Hansard records to examine which
politicians made supportive or aggressive statements toward other
politicians between 1979 and 1990, and \citet{Willis2017} examined how
politicians understood climate change. In New Zealand,
\citet{Curran2017} modelled the topics discussed between 2003 and 2016,
and \citet{Graham2016} examined unparliamentary language between 1890
and 1950.

Australian Hansard records have been analysed for various purposes, but
usually not at scale. For instance, \citet{Rasiah2010} examines Hansard
records for the Australian House of Representatives to examine whether
politicians attempted to evade questions about Iraq during February and
March 2003. \citet{GansLeigh2012} examined Australian Hansard records by
hand to associate mentions by politicians of certain public
intellectuals with neutral or positive sentiment.

The Australian parliaments generally make their Hansard records
available online as PDFs that can be downloaded. The Federal parliament
additionally makes XML records available for years between 1901 and 1980
as well as from 1997. There are roughly 65,000 \textbf{(UPDATE)} hansard
records available across the chambers of the state and federal
parliaments (Table 1) \textbf{(UPDATE NUMBERING)}. As with any
larger-scale data process, there are many issues with this dataset of
PDFs and the known ones are detailed in the Appendix.

@@

The PDFs were processed using the \texttt{PDFtools} R package of
\citet{Ooms2018pdftools}. A small proportion of the Hansard records had
not been put through a professional OCR process and although the Google
Tesseract engine as implemented by \citet{Ooms2018tesseract} provided
some useful data, these were not used in this analysis.

to extract these as text-based CSV records, and clean the records using
functions from the \texttt{Tidyverse} R package of
\citet{WickhamHadleyTidyverse}, the \texttt{Tidytext} R package of
\citet{SilgeRobinson2016} and the {[}INSERT OTHERS{]}. The result is a

@@

\includegraphics{svm-rmarkdown-article-example_files/figure-latex/topicsoverdocuments-1.pdf}
\includegraphics{svm-rmarkdown-article-example_files/figure-latex/topicsoverdocuments-2.pdf}

@@

\begin{figure}
\includegraphics[width=.49\linewidth]{svm-rmarkdown-article-example_files/figure-latex/topicsoverterms-1} \includegraphics[width=.49\linewidth]{svm-rmarkdown-article-example_files/figure-latex/topicsoverterms-2} \caption{Probability distributions over terms}\label{fig:topicsoverterms}
\end{figure}

@@

\subsection{Dataset issues}\label{dataset-issues}

Which PDFs are missing or have no content, etc.

\subsection{PDF to CSV issues}\label{pdf-to-csv-issues}

Insert graph of stop words over time.
